Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
Fixed motivation for first experiment

\subsection{Learning Rough Signals}
Consider a Gaussian process with a fixed kernel. Then, according to \cref{mod:cgpcm2}'s interpretation, the CGPCM should be able to learn this kernel. We compare the CGPCM and the GPCM.

@@

\subsection{Head-Related Impulse Response Estimation}
The head-related impulse response (HRIR) describes how the reception of sound by the ear depends on the position from which the sound originates. In particular, the received sound is convolved with the HRIR before it is sensed by the ear. Since this is exactly

>>>>

\subsection{Learning Rough Signals}
In \cref{subsec:roughness} we showed that the CGPCM models both smooth and rough isgnals, whereas the GPCM only models smooth signals. We perform two experiments that show the significance of this modelling capability.

@@

\subsection{Head-Related Impulse Response Estimation}
The head-related impulse response (HRIR) describes how the reception of sound by the ear depends on the position from which the sound originates. In particular, the received sound is convolved with the HRIR before it is sensed by the ear. We consider the problem of determining the HRIR given some signal sensed by the ear.
